%!TEX TS-program = xelatex
\documentclass{F32}

\begin{document}
\begin{center}
{\bf RESOURCE SHARING PLAN}
\end{center}

This work will generate new reagents and data that will be made freely available. Discoveries made as a result of this proposal will be published in peer-reviewed journals, presented at scientific conferences, and shared with other scientists and the community through open discussions. Information will only be withheld if it endangers chances of publication or communication to the community.

\subsubsection*{Chemical Characterization and Resources}
All original synthetic compounds and characterization obtained, including Riboglow probes and their associated NMR, UV/Vis, mass spectra, etc. will be stored in the Palmer lab indefinitely and will be distributed by the following plan:
\begin{itemize}
  \item Original and unprocessed spectra and chromatographs will be sent directly to requesting laboratories via email within 2 weeks of the original request.
  \item All processed spectra will be provided in the supporting information of published journal articles for continuous long term access.
  \item If available, small samples of material will be sent directly to requesting laboratories using standard express mailing services within 2 weeks of the original request.
\end{itemize}

\subsubsection*{DNA}
All original DNA reagents (including primers, plasmids, and libraries) will also be stored in the Palmer lab indefinitely and distributed by the following plan:
\begin{itemize}
  \item Genetic data, including high-throughput sequence reads will be submitted to the appropriate NIH-funded repositories including the NCBI BLAST database (https://blast.ncbi.nlm.nih.gov/Blast.cgi).
  \item Genetic constructs in the form of plasmids will be submitted to Addgene (www.addgene.org).
  \item DNA reagents will be will be sent directly to requesting laboratories using standard express mailing services within 2 weeks of the original request, so long as sufficient stocks remain available
\end{itemize}
I agree to deposit these resources into the appropriate repository as soon as possible but no later than within one year of the completion of the funded project period for the parent award or upon acceptance of the data for publication.

% AMY I am also attaching a resource sharing plan for a proposal I submitted back in 2013 so it's a little lame.  For resource sharing plans what I have seen is that sequences get deposited, constructs are shared with add gene, protocols are made available on websites and / or in detailed supplementary methods of publications, large datasets (RNAseq etc) are made available.  Chemical resources (such as probes you develop) are more challenging because it can be a substantial amount of work to synthesis.  I don't think there is an expectation to make available.  But, I think it would be reasonable to include a statement that you will make small aliquots of  compounds available to the community for test experiments.  Sequences of all riboswtiches will be published and constructs available from Addgene.

\end{document}
